GravExplain

### 2019-12-19 paper/paper_main.tex
added a couple of comments for later
a first go at the introduction text and adding bib file

% Note that AJP uses the same style as Phys. Rev. B (prb).
% The AIP Style Manual\cite{AIPstylemanual} is an indispensable reference on good physics writing, covering everything from planning and organization to standard spellings and abbreviations.
% Most important of all, please familiarize yourself with the AJP Statement of Editorial Policy,\cite{editorsite} which describes the types of manuscripts that AJP publishes and the audience for which AJP authors are expected to write.
% We look forward to receiving your submission to AJP.
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{float}
\usepackage{mathtools}
\usepackage{hyperref}

@@

@@

\section{Introduction}
GravExplain

@@

>>>>

% Note that AJP uses the same style as Phys. Rev. B (prb).
% The AIP Style Manual\cite{AIPstylemanual} is an indispensable reference on good physics writing, covering everything from planning and organization to standard spellings and abbreviations.
% Most important of all, please familiarize yourself with the AJP Statement of Editorial Policy,\cite{editorsite} which describes the types of manuscripts that AJP publishes and the audience for which AJP authors are expected to write.
% We look forward to receiving your submission to AJP.
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{float}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{hyperref}

@@

\newcommand{\han}{\textcolor{orange}}

@@

\section{Introduction}
\han{just had a first go at the introduction - not sure where we are aiming yet, so will probably end up re-writing!}

% general gw intro
In 2015 gravitational waves were observed for the first time from the merger of a binary black hole system. 
The observation, made by the Laser Interferometer Gravitational-wave Observatory~\citep[LIGO]{AdvancedLIGO:2015}, marked a breakthrough in modern astrophysics and provides a new means to observe the universe. 
Since then, the LIGO and Virgo~\cite{AdvancedVirgo:2015} observatories have made numerous detections of binary black hole~\cite{GW151226,GW170104,GW170814} and binary neutron star~\cite{GW170817,GW170817multi} mergers. 
With the increase in public interest in gravitational wave science, many gravitational wave research groups around the world have produced demonstrations and activities to explain this research to a general audience.
Activites range from online data analysis tutorials,~\cite{GWOSC:Online,LOSC:2015} hands-on demonstrations, phone apps,~\cite{LaserLabs:online,SciVR:online} and online games,~\cite{BlackHoleHunter:online} to exhibitions\han{add refs}, artistic interpretation, and musical performance \han{add refs}.

% what are gws and how do we detect them...
Gravitational waves are a prediction of Einstein's theory of general relativity. 
They are distrubances in spacetime caused by the accelleration of massive objects. 
The effect of them is to change distances; a ``stretch and squeeze'' effect. 
Observatories such as LIGO, Virgo and KAGRA (\han{reference}) are laser interferometers; they use the interference of laser light to measure changes in distance. 
The observatories themselves are extremely complex devices, however they are based on the Michelson interferometer. 
Table-top Michelson interferometers are commonly used by gravitational-wave research groups to demonstrate this science to non-specialist audiences~\cite{}\han{refs} and they are often used in undergraduate lab experiments~\cite{UgoliniEtAl:2019}.

% continuous gws
To date the network of gravitational wave observatories have observed short-duration transient signals~\cite{GWTC-1:2018}\han{update this ref and add GWOSC}. 
However, these observatories are also searching for continuous gravitational waves; persistent, periodic signals which should be present in the data for many months or years. 
A prime target for these searches are rotating neutron stars. 
So far many searches have been made of LIGO and Virgo data, however no detection has been made so far.

% overview
In this article we describe how a Michelson interferometer can be used to demonstrate the search for continuous waves to a general audience. 
The techniques used here are very similar to those used by the real continuous wave searches. 
In section X we describe...... \han{add this in at the end}

@@

\bibliographystyle{myunsrt}
\bibliography{ifoDemoBib}
